Compositional equivalences based on Open pNets

### 2020-03-16 2016-Weak-FH-Bisim/WeakBisim.tex
no example again

Fig. \ref{SimpleProt:Impl} shows the pNet model of the protocol implementation. When the $Medium$ detects an error (modeled by a local $\tau$ action), it sends back a $\texttt{m\_error}$ message to the $Sender$. The $Sender$ increments its local error counter $ec$, and resends the message (including $ec$) to the $Medium$, that will, eventually, transmit $m,ec$ to the $Receiver$.

>>>>

Fig. \ref{SimpleProt:Impl} shows the pNet model of the protocol implementation. When the $\symb{Medium}$ detects an error (modeled by a local $\tau$ action), it sends back a $\texttt{m\_error}$ message to the $\symb{Sender}$. The $\symb{Sender}$ increments its local error counter $ec$, and resends the message (including $ec$) to the $\symb{Medium}$, that will, eventually, transmit $m,ec$ to the $\symb{Receiver}$. Strictly speaking, as variables are local to each  state, we have two distinct $ec$ variables in the \textit{Sender} pLTS, one in state \texttt{s1}, another one in state \texttt{s2}, the value of the variable is updated along the transitions entering each of the two states.
